My passion for research in artificial intelligence first began as a desire to create automated systems that could accomplish tasks previously done only by humans.
As I entered the research world during my undergraduate studies, I soon found a component of AI that I enjoyed the most, machine learning.
Through my various research experiences, detailed in my resume, I learned that machine learning is a powerful tool expand the capabilities of AI and automation in general.
This has made me particularly interested in the research conducted in your lab, since the projects you embark upon all make use of machine learning to advance AI in new and exciting directions.

I believe that my abilities as a software engineer and experience in research can be of great value to the ML4AI lab.
Not only will my experience from developing and maintaining software code bases for many concurrent research projects be vital to the lab, but I believe that my experience in designing and analyzing algorithms, experimenting with design and implementation of the latest machine learning models, utilizing HPC resources, knowledge of web programming, and history of mentoring fellow students will all be vital resources to the ML4AI lab.
Additionally, I believe the most valuable resource I would bring to the lab is my experience as a software engineer and researcher on DARPA funded projects.
My past experience has prepared me for the fast-paced mode of work required to succeed on DARPA projects.
Likewise, my broad educational background in computer science and machine learning has made me an adaptable engineer who almost always has the experience required to chase the “moving-targets” and “updated goals” presented in DARPA projects.

Therefore, I would like to apply for the open position of R\&D Software Engineer III.
Thank you for your consideration and I look forward to hearing from you soon.
